---
output: github_document
editor_options: 
  chunk_output_type: console
params: 
  do_2017_article_details:
    value: TRUE
  do_2019_article_details:
    value: TRUE
  do_2020_article_details:
    value: TRUE
  do_2021_article_details:
    value: TRUE
  do_2022_article_details:
    value: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(htmltools)
library(magrittr)
```

```{r load-bib}
# load the bibliography. Article summaries depend on this
bib = RefManageR::ReadBib("assets/Articles.bib")

# get the unique journals I've published in based on bib file
# useful for filtering Google Scholar results later
my_journals = unique(unlist(lapply(bib, function(x) x$journal)))
```

```{r load-google-scholar-pubs}
# scrape my publications data from google scholar
my_pubs = scholar::get_publications("kembVusAAAAJ")

# keep only entries that share a journal with those found in my bib file
# this keeps only peer-reviewed articles found on google scholar and in bib
my_pubs = my_pubs[my_pubs$journal %in% my_journals,]

# replace any punctuation with a space: easier fuzzy matching later
my_pubs$title = stringr::str_replace_all(my_pubs$title, "[:punct:]", " ")
```

```{r set-italic-words}
# any string in this vector will be converted to italics
# in the article details portion of the output
em_words = c(
  "Misgurnus Anguillicaudatus",
  "Misgurnus anguillicaudatus",
  "M. anguillicaudatus",
  "Oncorhynchus tshawytscha",
  "O. mykiss",
  "Cyprinella caerulea",
  "Etheostoma brevirostrum",
  "Etheostoma ditrema",
  "Elassoma zonatum",
  "Tenacibaculum maritimum",
  "Piscine orthoreovirus"
  )
```

<!-- This document was created by knitting the Rmarkdown file README.rmd -->  

```{r define-img-objects}
# specify R objects that store the HTML code to insert one of the icons used.
# note how each img has two options: one for each light and dark themes

# a closed lock: used for denoting paywall articles/private repos
lock_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock-dark.svg#gh-dark-mode-only", height = "15")
)

# an open lock: used for denoting open-access articles/public repos
open_lock_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock-open.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock-open-dark.svg#gh-dark-mode-only", height = "15")
)

# inline versions of these lock icons
lock_img_inline = HTML("<img src=https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock.svg#gh-light-mode-only height=15/><img src=https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock-dark.svg#gh-dark-mode-only height=15/>")
open_lock_img_inline = HTML("<img src=https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock-open.svg#gh-light-mode-only height=15/><img src=https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/lock-open-dark.svg#gh-dark-mode-only height=15/>")

# a closed book: used to represent a journal
book_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/book.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/book-dark.svg#gh-dark-mode-only", height = "15")
)

# an open book: used to represent an abstract
book_reader_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/book-reader.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/book-reader-dark.svg#gh-dark-mode-only", height = "15")
)

# code icon: used to represent locations of archived/open source code/data
code_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/code.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/code-dark.svg#gh-dark-mode-only", height = "15")
)

# users icon: used to represent author list
users_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/users.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/users-dark.svg#gh-dark-mode-only", height = "15")
)

# quote icon: used to represent how to cite
quote_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/quote-left.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/quote-left-dark.svg#gh-dark-mode-only", height = "15")
)

# comment icon: used to represent citations
comment_img = tagList(
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/comment.svg#gh-light-mode-only", height = "15"),
  img(src = "https://raw.githubusercontent.com/bstaton1/bstaton1/master/assets/comment-dark.svg#gh-dark-mode-only", height = "15")
)
```

```{r greeting}
# create HTML code to build the greeting header
tagList(
  h1("Welcome to My GitHub Profile", align = 'center'),
  h3("I'm a Quantitative Fisheries Scientist", align = 'center'),
  p(em("with a focus on assessment, fishery management, and conservation of Pacific salmon"), align = 'center')
)
```

```{r about-me-links}
# create the HTML code to build img.shields.io badges for each of my personal links

# my google scholar info
google_scholar = a(
  href = "https://scholar.google.com/citations?user=kembVusAAAAJ&hl=en",
  img(src = "http://img.shields.io/badge/-Google Scholar-2088FF?style=flat&logo=google-scholar&logoColor=ffffff",
      alt = "GoogleScholar"
  )
)

# my research gate info
research_gate = a(
  href = "https://www.researchgate.net/profile/Benjamin-Staton",
  img(src = "http://img.shields.io/badge/-ResearchGate-2088FF?style=flat&logo=researchgate&logoColor=ffffff",
      alt = "ResearchGate"
  )
)

# my orcid info
orcid = a(
  href = "https://orcid.org/0000-0002-2342-3482",
  img(src = "http://img.shields.io/badge/-ORCID-2088FF?style=flat&logo=ORCID&logoColor=ffffff",
      alt = "ORCID"
  )
)

# my publons info
publons = a(
  href = "https://publons.com/researcher/3415841/benjamin-staton",
  img(src = "http://img.shields.io/badge/-Publons-2088FF?style=flat&logo=Publons&logoColor=ffffff",
      alt = "Publons"
  )
)

# my twitter info
twitter = a(
  href = "https://twitter.com/bstat0n",
  img(src = "http://img.shields.io/badge/-Twitter-2088FF?style=flat&logo=Twitter&logoColor=ffffff",
      alt = "Twitter"
  )
)

# combine and return them
tagList(
  p(google_scholar, research_gate, orcid, publons, twitter, align = "center")
)
```

## My Interests

* **Population dynamics** and models that describe them
* **Methods for counting animals** (generally :fish:) and the models we use to make sense of the data
* **Bayesian analysis** as a means to quantify knowledge and uncertainty
* **State-space models** as a means to disentangle biological and observational processes
* **Transparent and data-driven decision processes** because regardless of the outcome, it should always be clear why a choice was made
* **Reproducible workflows** because analyses are rarely ever \"finished\"

For more information about me and the things I work on, you can view my [curriculum vitae](<https://github.com/bstaton1/bstaton1/blob/master/assets/CV.pdf>).

I also operate a small consulting company (Quantitative Ecological Services, LLC) -- please email me at <bstaton.qes@gmail.com> for more details.

## Commonly Used Tools/Languages

> _In decreasing order of how awful it would be if they were to disappear_

```{r used-tools}
# create the HTML code to build img.shields.io badges for each of my used software tools

# google
Google = a(
  href = "https://www.google.com",
  img(src = "http://img.shields.io/badge/-Google-2088FF?style=flat&logo=Google&logoColor=ffffff",
      alt = "Google"
  )
)

# R
R = a(
  href = "https://www.r-project.org/",
  img(src = "http://img.shields.io/badge/-R-2088FF?style=flat&logo=R&logoColor=ffffff",
      alt = "R"
  )
)

# RStudio
RStudio = a(
  href = "https://rstudio.com/",
  img(src = "http://img.shields.io/badge/-RStudio-2088FF?style=flat&logo=RStudio&logoColor=ffffff",
      alt = "RStudio"
  )
)

# JAGS
JAGS = a(
  href = "http://mcmc-jags.sourceforge.net/",
  img(src = "http://img.shields.io/badge/-JAGS-2088FF?style=flat",
      alt = "JAGS"
  )
)

# GitHub
GitHub = a(
  href = "https://github.com/bstaton1",
  img(src = "http://img.shields.io/badge/-GitHub-2088FF?style=flat&logo=github&logoColor=ffffff",
      alt = "GitHub"
  )
)

# markdown
markdown = a(
  href = "https://www.markdownguide.org/",
  img(src = "http://img.shields.io/badge/-markdown-2088FF?style=flat&logo=markdown&logoColor=ffffff",
      alt = "markdown"
  )
)

# LaTeX
LaTeX = a(
  href = "https://www.latex-project.org/",
  img(src = "http://img.shields.io/badge/-LaTeX-2088FF?style=flat&logo=latex&logoColor=ffffff",
      alt = "LaTeX"
  )
)

# Bash
Bash = a(
  href = "https://www.gnu.org/software/bash/",
  img(src = "http://img.shields.io/badge/-Bash-2088FF?style=flat&logo=gnu-bash&logoColor=ffffff",
      alt = "Bash"
  )
)

# combine and return them
tagList(
  p(Google, R, JAGS, RStudio, GitHub, markdown, LaTeX, Bash)
)
```

## Tools I\'d Like to Learn

```{r to-learn}
# create the HTML code to build img.shields.io badges for each of my used software tools

# Stan
Stan = a(
  href = "https://mc-stan.org/",
  img(src = "http://img.shields.io/badge/-Stan-2088FF?style=flat",
      alt = "Stan"
  )
)

# TMB
TMB = a(
  href = "https://github.com/kaskr/adcomp/wiki",
  img(src = "http://img.shields.io/badge/-TMB-2088FF?style=flat",
      alt = "TMB"
  )
)

# combine and return them
tagList(
  p(Stan, TMB)
)
```

## Current Projects

```{r project-help-text}
p(open_lock_img, em("and"), lock_img, em("denote public and private repositories, respectively."))
```

#### Research

* [GR-sslcm](<https://github.com/bstaton1/GR-sslcm>) `r lock_img_inline`: Development of a state-space life cycle model for spring Chinook salmon in the Grande Ronde River basin of northeastern Oregon. _Under active development_.
* [LKG-RRS-ms-analysis]() `r lock_img_inline`: Analysis for a manuscript that compares the reproductive success (i.e., number of progeny that survive to various stages) of wild-spawning spring Chinook salmon that differ in a range of characteristics including origin, sex, arrival timing, and size. _Under active development_.
* [inseason-voi-ms-analysis](<https://github.com/bstaton1/inseason-voi-ms-analysis>) `r lock_img_inline`: Analysis for a manuscript that investigates the Value of Information of different data sources used during in-season decision-making regarding total allowable harvest for large in-river subsistence salmon fisheries. _Under active development_.
* In-season estimation and prediction of effort and harvest for lower Kuskokwim River subsistence salmon fisheries
  * [KuskoHarvEst](<https://github.com/bstaton1/KuskoHarvEst>) `r open_lock_img_inline`: R package containing tools and an associated workflow for estimating effort and harvest given monitoring data as inputs. Tools can be executed via code-only or interactive (point-and-click) workflows; the interactive workflow automates summary report generation using [Rmarkdown](https://rmarkdown.rstudio.com/) and built-in templates. _Development considered complete at present_.
  * [KuskoHarvData](<https://github.com/bstaton1/KuskoHarvData>) `r open_lock_img_inline`: R package containing historical data and estimates derived using \'KuskoHarvEst\'. _Under active development_.
  * [KuskoHarvPred](<https://github.com/bstaton1/KuskoHarvPred>) `r open_lock_img_inline`: R package containing tools for reproducibly conducting regression analyses that seek to predict critical fishery outcomes arising from proposed fishing opportunities. _Under active development_.

#### General Purpose R Packages

```{r pkg-downloads-fn, eval = FALSE}
cran_dl_badge = function(pkg, start_date, type = "total") {
  # query updated data
  out = cranlogs::cran_downloads(pkg,
                                 from = start_date,
                                 to = lubridate::today() - 1)
  
  # build the basic URLs with placeholders
  badge_url = "https://img.shields.io/badge/TYPE%20CRAN%20Downloads-NUMBER-blue"
  pkg_url = "https://CRAN.R-project.org/package=PKG"
  
  # type must be either 'total' or 'monthly'
  if (!(type %in% c("total", "monthly"))) {
    stop ("type must be one of 'total' or 'monthly'")
  }
  
  # calculate the download stats based on the interval
  if (type == "total") {
    value = paste0(round(sum(out$count)/1000, 1), "k")
    Type = "Total"
  } else {
    out$mon_year = paste0(lubridate::month(out$date), "-", lubridate::year(out$date))
    value = round(mean(tapply(out$count, out$mon_year, sum)))
    Type = "Monthly"
  }

  # replace the placeholders with the calculated values
  badge_url = gsub("TYPE", Type, badge_url)
  badge_url = gsub("NUMBER", value, badge_url)
  
  # build the package URL
  pkg_url = gsub("PKG", pkg, pkg_url)
  
  # build the HTML code to render
  htmltools::a(href = pkg_url, img(src = badge_url, alt = "CRAN Downloads"))
}

cran_dl_badge("postpack", "2020-09-17", "monthly")
cran_dl_badge("postpack", "2020-09-17", "total")
```

* [postpack](<https://github.com/bstaton1/postpack>) ([website](https://bstaton1.github.io/postpack/)) `r open_lock_img_inline`: Assortment of tools for working with R objects of class `mcmc.list`. _Under active development_. 
* [msdown](<https://github.com/bstaton1/msdown>) `r lock_img_inline`: Template and utilities for writing clean, reproducible, and version controllable manuscripts built off [bookdown](<https://pkgs.rstudio.com/bookdown>). _Under active development_.

## Peer-Reviewed Journal Articles

```{r article-help-text}
p(em("Click the title of each article to see more information."), open_lock_img, em("and"), lock_img, em("denote open-access and paywall articles, respectively."))
```

```{r article-fns, eval = TRUE, message = FALSE}
my_em = function(x) {
  for (i in 1:length(em_words)) {
    x = stringr::str_replace_all(x, em_words[i], paste0("<em>", em_words[i], "</em>"))
  }
  return(x)
}

my_name_strong = function(x) {
  stringr::str_replace(x, "B. A. Staton", "<strong>B. A. Staton</strong>") %>%
    stringr::str_replace("Staton, B. A,", "<strong>Staton, B. A,</strong>") %>%
    stringr::str_replace("Staton, B,", "<strong>Staton, B,</strong>") %>%
    stringr::str_replace("B. Staton", "<strong>B. Staton</strong>")
}

prep_bibentry = function(key) {
  this_bib = bib[key]
  
  # create a "pretty citation" from the bibentry
  old_opts = RefManageR::BibOptions()
  on.exit(RefManageR::BibOptions(old_opts))
  RefManageR::BibOptions(max.names = 20, style = "text", bib.style = "authoryear", dashed = FALSE)
  str_bib = format(this_bib)
  
  # remove any line breaks portion
  str_bib = stringr::str_replace_all(str_bib, "\\n",  " ")
  str_bib = stringr::str_replace_all(str_bib, "\\\\textendash ",  "&#8211;")
  str_bib = stringr::str_remove_all(str_bib, "_")
  
  # extract author list: do it this way so first and middle names are abbreviated
  authors = stringr::str_extract(str_bib, "^.+\\([:digit:]") %>%
    stringr::str_remove(" \\([:digit:]")
  
  # extract the title: do it this way so capitalization and {} are handled properly
  # title = stringr::str_extract(str_bib, "“.+”") %>%
  #   substr(2, nchar(.)-1)
  title = stringr::str_extract(str_bib, "\\). .+In\\:") %>%
    stringr::str_remove("\\). ") %>%
    stringr::str_remove(" In\\:$") %>%
    substr(2,nchar(.)-2)
  
  # extract the abstract from online
  # abstract = tryCatch(rcrossref::cr_abstract(this_bib$doi), error = function(e) "Abstract not found on CrossRef. Consult the DOI link shown above for the abstract.")
  abstract = this_bib$abstract
  abstract = stringr::str_replace_all(abstract, "\\\\textendash ",  "&#8211;")
  abstract = stringr::str_replace_all(abstract, "\\\\textdegree ",  "&#176;")
  abstract = stringr::str_replace_all(abstract, "``",  '"')
  abstract = stringr::str_replace_all(abstract, "''",  '"')
  abstract = stringr::str_replace_all(abstract, "O2 kg-1h-1", "O<sub>2</sub> kg<sup>-1</sup>h<sup>-1</sup>")
  abstract = stringr::str_replace_all(abstract, "Topt", "<em>T</em><sub>opt</sub>")
  abstract = stringr::str_replace_all(abstract, "Tlow", "<em>T</em><sub>low</sub>")
  abstract = stringr::str_replace_all(abstract, "Tup", "<em>T</em><sub>up</sub>")
  abstract = stringr::str_replace_all(abstract, "Tbreadth", "<em>T</em><sub>breadth</sub>")
  abstract = stringr::str_replace_all(abstract, "\\{\\$<\\$\\}", "&#60;")
  abstract = stringr::str_replace_all(abstract, "\\\\%", "%")
  
  # obtain the citation count: cross ref
  cites_crossref = rcrossref::cr_citation_count(this_bib$doi)$count
  cites_crossref = ifelse(is.null(cites_crossref), NA, cites_crossref)
  
  # obtain the citation count: google scholar
  title_join = stringr::str_replace_all(title, "&#8211;", "–")
  title_join = stringr::str_replace_all(title_join, "[:punct:]", " ")
  cites_gscholar = my_pubs[stringdist::amatch(tolower(title_join), tolower(my_pubs$title)),"cites"]
  
  # build the output list
  list(
    authors = authors,
    title = title,
    year = this_bib$year,
    journal = this_bib$journal,
    volume = this_bib$volume,
    number = this_bib$number,
    pages = this_bib$pages,
    doi = this_bib$doi,
    abstract = abstract,
    cites_crossref = cites_crossref,
    cites_gscholar = cites_gscholar
  )
}

build_journal_name = function(bib_data) {
  em(paste0(bib_data$journal, ","))
}

build_journal_info = function(bib_data) {
  volume_use = ifelse(!is.null(bib_data$volume), bib_data$volume, "")
  number_use = ifelse(!is.null(bib_data$number), paste0("(", bib_data$number, ")"), "")
  pages_use = ifelse(!is.null(bib_data$pages), bib_data$pages, "")
  pages_use = stringr::str_replace(pages_use, "--", "-")
  number_pages_sep = ifelse(pages_use == "", "", ": ")
  out = paste0(volume_use, number_use, number_pages_sep, pages_use)
  if (out == "") {
    out = "In Press"
  }
  return(out)
}

build_doi_badge = function(doi) {
  if (!is.null(doi)) {
    url = paste0("https://doi.org/", doi)
    badge = paste0("https://zenodo.org/badge/DOI/", doi, ".svg")
    a(href = url, img(src = badge, alt = "DOI"))
  }
}

article_details = function(key, open_access = FALSE, code_repo = NULL, code_doi = NULL) {
  
  # prepare the bibliographic data
  bib_data = prep_bibentry(key)
  
  # set the lock image to use
  if (open_access) {
    lock_use = open_lock_img
  } else {
    lock_use = lock_img
  }
  
  if (!is.null(code_repo)) {
    repo = tagList(strong("Repository:"), a(href = paste0("https://github.com/", code_repo), code_repo), br())
  } else {
    repo = tagList(strong("Repository:"), "Not Available", br())
  }
  
  if (!is.null(code_doi)) {
    archive = tagList(strong("Archive:"), build_doi_badge(code_doi))
  } else {
    archive = tagList(strong("Archive:"), "Not Available")
  }
  
  tags$details(
    tags$summary(lock_use, strong(HTML(my_em(bib_data$title)))),
    p(),
    
    tags$ul(
      tagList(book_img, strong(em("JOURNAL"))),
      tags$ul(
        p(build_journal_name(bib_data), build_journal_info(bib_data), br(), build_doi_badge(bib_data$doi))
      ),
      
      tagList(users_img, strong(em("AUTHORS"))),
      tags$ul(
        p(HTML(my_name_strong(bib_data$authors)))
      ),
    
      tagList(book_reader_img, strong(em("ABSTRACT"))),
      tags$ul(
        p(HTML(my_em(bib_data$abstract)), align = "justify")
      ),

      tagList(code_img, strong(em("CODE/DATA"))),
      tags$ul(
        repo,
        archive
      ),
      p(),

      tagList(comment_img, strong(em("CITATIONS"))),
      tags$ul(
        tagList(strong("Crossref: "), bib_data$cites_crossref, br()),
        tagList(strong("Google Scholar: "), bib_data$cites_gscholar)
      )
    ),
    hr()
  )
}
```

### 2022

```{r 2022-articles, eval = params$do_2022_article_details}
# Lookingglass Creek RRS paper with Hayley
article_details(
  key = "nuetzel-etal-2022",
  open_access = TRUE,
  code_repo = "bstaton1/LKG-RRS",
  code_doi = "10.5281/zenodo.6621724"
)

# ETS-vs-temperature GAM paper with Lindsay
article_details(
  key = "horne-etal-2022",
  open_access = FALSE,
  code_repo = "bstaton1/ETS-vs-temp-ms-analysis",
  code_doi = "10.5281/zenodo.7187078"
)

# Yukon Chinook multi-stock analysis
article_details(
  key = "connors-etal-2022",
  open_access = FALSE, 
  code_repo = "brendanmichaelconnors/yukon-chinook-diversity",
  code_doi = "10.5281/zenodo.6625526"
)

# infectious agents in BC Chinook/Coho
article_details(
  key = "bass-etal-2022",
  open_access = TRUE, 
  code_repo = NULL,
  code_doi = NULL
)

# snorkel detection probability
article_details(
  key = "staton-etal-2022",
  open_access = FALSE, 
  code_repo = "bstaton1/snk-eff-ms-analysis",
  code_doi = "10.5281/zenodo.3928691"
)
```

### 2021

```{r 2021-articles, eval = params$do_2021_article_details}
# sire age and minijacks
article_details(
  key = "galbreath-etal-2021", 
  open_access = TRUE,
  code_repo = "bstaton1/cesrf-minijack-rates",
  code_doi = "10.5281/zenodo.4730682"
)

# escapement quality
article_details(
  key = "staton-etal-2021",
  open_access = FALSE,
  code_repo = "bstaton1/esc-qual-ms-analysis",
  code_doi = "10.5281/zenodo.4382757"
)

# spatiotemporal growth patterns
article_details(
  key = "kaylor-etal-2021",
  open_access = FALSE,
  code_repo = "mjkaylor/JoAE_data_archive",
  code_doi = "10.5281/zenodo.4627774"
)
```

### 2020

```{r 2020-articles, eval = params$do_2020_article_details}
# multi-stock SRA models
article_details(
  key = "staton-etal-2020",
  open_access = FALSE,
  code_repo = "bstaton1/mixed-stockSRA",
  code_doi = "10.5281/zenodo.3375006"
)

# harvest-biodiversity trade-offs
article_details(
  key = "connors-etal-2020",
  open_access = FALSE,
  code_repo = "brendanmichaelconnors/Kusko-harvest-diversity-tradeoffs",
  code_doi = "10.5281/zenodo.3375124"
)
```

### 2019

```{r 2019-articles, eval = params$do_2019_article_details}
# in-season updates
article_details(
  key = "staton-catalano-2019",
  open_access = FALSE,
  code_doi = "inseason-update-ms-analysis",
  code_repo = "10.5281/zenodo.1467683"
)

# telemetry
article_details(
  key = "moses-etal-2019",
  open_access = TRUE,
  code_repo = NULL,
  code_doi = "10.3996/082018-JFWM-074.S1"
)
```

### 2017

```{r 2017-articles, eval = params$do_2017_article_details}
# run timing forecast
article_details(
  key = "staton-etal-2017",
  open_access = FALSE,
  code_repo = NULL,
  code_doi = NULL
)

# AFS meetings
article_details(
  key = "dippold-etal-2017", 
  open_access = FALSE,
  code_repo = NULL,
  code_doi = NULL
)

# loaches
article_details(
  key = "white-etal-2017", 
  open_access = TRUE,
  code_repo = NULL,
  code_doi = NULL
)

# integrated vs. sequential
article_details(
  key = "staton-etal-2017a", 
  open_access = FALSE,
  code_repo = NULL,
  code_doi = NULL
)
```

```{r footnote}
p(
  tagList(
    tags$sub(
      tags$sup(
        em(
          "This file was created by knitting",
          a("README.Rmd", href = "https://github.com/bstaton1/bstaton1/blob/master/README.Rmd"),
          "which makes heavy usage of R packages:",
          a("htmltools", href = "https://rstudio.github.io/htmltools/"), ",",
          a("stringr", href = "https://stringr.tidyverse.org/"), ",",
          a("RefManageR", href = "https://docs.ropensci.org/RefManageR/"), ",",
          a("rcrossref", href = "https://docs.ropensci.org/rcrossref/"), ", and",
          a("scholar", href = "https://CRAN.R-project.org/package=scholar")
        )
      )
    ),
    br(),
    tags$sub(
      tags$sup(
        em(
          HTML("&#169;"), "Ben Staton under the ", a("MIT license", href = "https://github.com/bstaton1/bstaton1/blob/master/LICENSE")
        )
      )
    ),
    br(),
    tags$sub(
      tags$sup(
        em("Updated", Sys.Date())
      )
    )
  ),
  align = "center"
)
```
